Binocular integration of chromatic and luminance signals

### 2024-04-02 manuscript.qmd
Last try before I get frustrated and give up

if (processdata>0){
  install_python(version="3.9.19")
  use_python_version("3.9.19")
  # use_python('/usr/bin/python3')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

A useful framework for understanding binocular signal processing is the two-stage gain control model of binocular combination introduced by @Meese2006. This model features interocular suppression between monocular channels, followed by binocular summation. The model accounts well for the pattern of contrast discrimination ('dipper') functions for four distinct ocular configurations [see also @Georgeson2016], illustrated in @fig-exampledips. In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance. Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy. The binocular condition is the same, except that the same stimuli are shown to both eyes. In the half-binocular condition the pedestal is shown to both eyes, but the target increment shown only to one eye. Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.

>>>>

if (processdata>0){
  # install_python(version="3.9.19")
  # use_python_version("3.9.19")
  use_python('/usr/bin/python3.9')
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # py_install('pip')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

A useful framework for understanding binocular signal processing is the two-stage gain control model of binocular combination introduced by @Meese2006. This model features interocular suppression between monocular channels, followed by binocular summation. The model accounts well for the pattern of contrast discrimination ('dipper') functions for four distinct ocular configurations [see also @Georgeson2016], illustrated in @fig-exampledips. In the monocular condition, participants must discriminate between stimuli of two contrasts (a 'pedestal', and a 'pedestal plus target') that are both presented to one eye, whilst the other eye views mean luminance. Threshold is defined as the minimum target contrast required to make this judgement with 75% accuracy. The binocular condition is the same, except that the stimuli are shown to both eyes. In the half-binocular condition the pedestal is shown to both eyes, but the target increment is shown only to one eye. Finally, the dichoptic condition involves presenting the pedestal to one eye, and the target increment to the other eye.
